On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-21 paper/paper.tex
Small wibble

% Say why it is an interesting problem
  However, capturing traditional control flow in an deeply embedded domain specific language
  would allow for writing programs in a natural style, and enables the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves

>>>>

% Say why it is an interesting problem
  However, capturing traditional control flow in an deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
